---
title: "Journal Challenge 2a"
author: "David Hackenberger"
date: "2020-11-026"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    toc_depth: 3
    #code_folding: hide
---

# Challange Data Aquisition
## Challange Part 1
We want to compile an overview of drinks based on the liquor gin.
For this we use the online database thecocktaildb and the provided API.

### Install libraries
```{r}
library(RSQLite)
library(tidyverse)
library(glue)
library(jsonlite)
library(httr)
library(xopen)  
library(data.table)
```

### Website used: https://www.thecocktaildb.com
```{r}
TheCocktailDB_home_url <- "https://www.thecocktaildb.com"
xopen(TheCocktailDB_home_url)
```

#### Retrieve data via an API
The API is free to use with an Academic License Key with limited functionality.
Access is via the link: https://www.thecocktaildb.com/api/json/v1/ followed by the license key, the desired database processing, a class and an element.
Example: https://www.thecocktaildb.com/api/json/v1/1/search.php?s=margarita searches a cocktail by name.

Since we can only retrieve limited lists from the database under the free license, we build a function that we execute multiple times and thus combine our own database.

#### Define function
```{r}
                    #We will need the following variables:
                    #key    <- 1        # Academic Token
                    #process  <- "filter"   # list, filter, search, lookup
                    #operator  <- "i"      # i: ingredients, i: idDrink, iid: ingrediants by ID
                    #element   <- "Gin"   # "list" oder "Benennung"
thecocktaildb_JSON <- function(key,process,operator,element){
  url <- modify_url(url = TheCocktailDB_home_url, path = glue("/api/json/v1/{key}/{process}.php?{operator}={element}"))
  resp <- GET(url)
  stop_for_status(resp)
}
```

#### Building the dataset
First we get a list of contents to check how the spirit Gin is listed in the database.
```{r}
list_of_ingrediants_tbl <- thecocktaildb_JSON(1,"list","i","list") %>%
# Convert
  .$content %>% 
  rawToChar() %>% 
  fromJSON()%>%
  .$drinks %>%
  as_tibble() %>%
  # Renaming
  rename("Ingrediants"       = "strIngredient1")
  
list_of_ingrediants_tbl$Ingrediants
```

Gin is the third entry in the contents list and is spelled "Gin".
Now let's call up a list of all drinks with the ingredient Gin.
```{r}
list_of_Gin_drinks_tbl <- thecocktaildb_JSON(1,"filter","i",list_of_ingrediants_tbl$Ingrediants[3]) %>%
# Convert
  .$content %>% 
  rawToChar() %>% 
  fromJSON() %>%
  .$drinks %>%
  as_tibble() %>%
  #Clean
  select(-strDrinkThumb) %>%
  # Renaming
  rename("Drink"       = "strDrink") %>%
  rename("ID"       = "idDrink")
```

Now we have the titles of the gin drinks and can use there ids to retrieve further information from the database.
```{r}
get_Details <- function(id){
drink_details_tbl <- thecocktaildb_JSON(1,"lookup","i",id) %>% 
  # Convert
  .$content %>% 
  rawToChar() %>% 
  fromJSON() %>% 
  .$drinks %>%
  as_tibble() %>% 
  #Clean
  select(strDrink,idDrink,strCategory,strGlass,
         strInstructions,starts_with("strIngredient"),starts_with("strMeasure"))
}

library(furrr)     # Parallel Processing using furrr (iteration)
plan("multiprocess")

Gin_drinks_tbl <- future_map(list_of_Gin_drinks_tbl$ID, get_Details) %>% 
  rbindlist(use.names=TRUE, fill=FALSE, idcol=NULL)

#Rename, beacuse most of the collums start with str
colnames(Gin_drinks_tbl) = gsub("str", "", colnames(Gin_drinks_tbl))
```

#### Resulting Dataset
Now we have an extensive data set of gin drinks with ingredients, recipe and quantities.
```{r}
print(Gin_drinks_tbl, n = 10)
```
  
  
