---
title: "Journal Challenge 3"
author: "David Hackenberger"
date: "2020-12-02"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 3
    #code_folding: hide
---

# Challange Data Wrangling
## Getting started
### Install libraries
```{r}
# Tidyverse
library(tidyverse)

# Importing Data
library(vroom)

# Data Table
library(data.table)

# View data
library(kableExtra)
```

### Define structure for importing
We need to import the tables:
assignee, patent, patent_assignee to link the first two ans uspc.

```{r}
# To speed up your processing, you can select col_skip() as a “datatype” to only read the columns of the data into R, that you will need for your analysis.
# Column structure for the assignee table
col_types_assignee <- list(
  id = col_character(),
  type = col_integer(),
  name_first = col_skip(), # We don't need these two lines, bevause we are only intersted in the companies
  name_last = col_skip(),
  organization = col_character()
)

# Column structure for the patent table
col_types_patent <- list(
  id = col_character(),
  type = col_skip(), # does not matter
  number = col_character(),
  country = col_skip(), # its always US and we are filtering by the company
  date = col_date("%Y-%m-%d"),
  abstract = col_skip(), # does not matter
  title = col_skip(), # does not matter
  kind = col_skip(), # does not matter
  num_claims = col_skip(), # we are not interested in the length
  filename = col_skip(), # does not matter
  withdrawn = col_skip() # does not matter
)

# Column structure for the patent_assigne table
col_types_patent_assignee <- list(
  patent_id = col_character(),
  assignee_id = col_character(),
  location_id = col_skip() # does not matter, we get the locatino by the company
)

# Column structure for the uspc table
col_types_uspc <- list(
  uuid = col_skip(),
  patent_id = col_character(),
  mainclass_id = col_character(),
  subclass_id = col_skip(), # does not matter, because we are only loocking for the main calsses
  sequence = col_skip() # does not matter
)
  
# Column structure for maincalss_current table
col_types_maincalss_current <- list(
  id = col_character(),
  title = col_character()
)
```

### Enable parallel computing for faster processing
```{r}
# Parallel processing
library(parallel)
library(doMC)

# Detect the cores available in the computer
numCores <- detectCores()

# Register the cores for use by R
registerDoMC(cores = numCores)
```

### Importing
```{r}

# import the assignee table
assignee_tbl <- vroom(
            file       = "Raw_Data/Data_wrangling/assignee.tsv", 
            delim      = "\t", 
            col_types  = col_types_assignee,
            na         = c("", "NA", "NULL")
        )

# import the patent table
patent_tbl <- vroom(
            file       = "Raw_Data/Data_wrangling/patent.tsv", 
            delim      = "\t", 
            col_types  = col_types_patent,
            na         = c("", "NA", "NULL")
        )

# import the patent_assignee table
patent_assignee_tbl <- vroom(
            file       = "Raw_Data/Data_wrangling/patent_assignee.tsv", 
            delim      = "\t", 
            col_types  = col_types_patent_assignee,
            na         = c("", "NA", "NULL")
        )

# import the uspc table
uspc_tbl <- vroom(
            file       = "Raw_Data/Data_wrangling/uspc.tsv", 
            delim      = "\t", 
            col_types  = col_types_uspc,
            na         = c("", "NA", "NULL")
        )

# import uspc calss description with mainclass_current
mainclass_current_tbl <- vroom(
            file       = "Raw_Data/Data_wrangling/mainclass_current.tsv", 
            delim      = "\t", 
            col_types  = col_types_maincalss_current,
            na         = c("", "NA", "NULL")
        )
```

### Check out the Data
```{r}
glimpse(assignee_tbl)
glimpse(patent_tbl)
glimpse(patent_assignee_tbl)
glimpse(uspc_tbl)
glimpse(mainclass_current_tbl)
```

### Convert to data.table
```{r}
registerDoMC(cores = numCores)
# assignee
setDT(assignee_tbl)
class(assignee_tbl)
# patent
setDT(patent_tbl)
class(patent_tbl)
# patent_assignee
setDT(patent_assignee_tbl)
class(patent_assignee_tbl)
# uspc (needed for third question)
setDT(uspc_tbl)
class(uspc_tbl)
# mainclasses
setDT(mainclass_current_tbl)
class(mainclass_current_tbl)
```

## 1. Question 1
Patent Dominance: What US company / corporation has the most patents? List the 10 US companies with the most assigned/granted patents.
How to get there: 
1. Key assignee_id in assignee and patent_assignee table
2. Join assignee and patent_assignee table
3. Group by key (assignee_id) and count patent_id and order descending
### Data Wrangling
```{r}
# 1. Key assignee_id in assignee and patent_assignee table
setkey(assignee_tbl, "id")
setkey(patent_assignee_tbl, "assignee_id")
# 2. Join assignee and patent_assignee table
Q1_data <- merge(x = patent_assignee_tbl, y = assignee_tbl, 
                       by.x    = "assignee_id",
                       by.y    = "id",
                       all.x = TRUE, 
                       all.y = FALSE)
# 3. Filter by us company and only existig patents, then group by patent to collect is a patent is named multiple times. After that group by organizatino and get the number of entries (= how many patents are there for each company) and order in descending.
N_of_patents_by_US_comp <- Q1_data[type == 2 & !is.na(patent_id), .(organization,assignee_id), by = patent_id][,.N,by=organization][order(-N),.(organization,patent_number=N)]
```

### View Results
```{r results = "asis"}
options(knitr.table.format = "html") 
kbl(N_of_patents_by_US_comp[1:10, ]) %>%
  kable_styling(bootstrap_options = c("striped", "hover"),fixed_thead = T)
```

## 2. Question 2
Recent patent acitivity: What US company had the most patents granted in 2019? List the top 10 companies with the most new granted patents for 2019.
How we get there:
1. We enlagre the tabel from question by the patent information when the patents where granted
2. filter like in question one + by year = 2019
### Data Wrangling
```{r}
# 1. Key assignee_id in assignee and patent_assignee table
# setkey(patent_tbl, "number")

# 2. Join Q1_data with patent table
#2.1 shorten the patent table and already filter biy 2019
patent_data_2019 <- patent_tbl[year(date) == 2019,.(date),keyby = number]
Q2_data <- merge(x = Q1_data, y = patent_data_2019, 
                       by.x    = "patent_id",
                       by.y    = "number",
                       all.x = TRUE, 
                       all.y = FALSE)
# 3. Filter by us company, only existig patents and year != NA, then group by patent to collect is a patent is named multiple times. After that group by organizatino and get the number of entries (= how many patents are there for each company) and order in descending.
patent_activity_by_US_comp_2019 <- Q2_data[type == 2 & !is.na(patent_id) & !is.na(date), .(organization,assignee_id), by = patent_id][,.N,by=organization][order(-N),.(organization,granted_patents_2019=N)]
```

### View Results
```{r results = "asis"}
options(knitr.table.format = "html") 
kbl(patent_activity_by_US_comp_2019[1:10, ]) %>%
  kable_styling(bootstrap_options = c("striped", "hover"),fixed_thead = T)
```

## 3. Question 3
Innovation in Tech: What is the most innovative tech sector? For the top 10 companies (worldwide) with the most patents, what are the top 5 USPTO tech main classes?
How we get there:
1. Key the uspc table by patent_id
2. Cut the data from Question 1 and get back the patents by merging with patent table
3. Join the new table and uspc by patent_id
5. Merge with maincalsses_current to get info about uspc calsses
6. Group by uspc classes, count entries and order descending including the description of the mainclasses
### Data Wrangling
```{r}
# 1. Key the uspc table by patent_id
Q3_uspc_tbl <- uspc_tbl[!is.na(patent_id),.(mainclass_id),keyby = patent_id]
setkey(mainclass_current_tbl, "id")
setkey(Q1_data, "organization")
# 2. Cut the data from Question 1
top_10_us_companies_data <- N_of_patents_by_US_comp[2:10]
setkey(top_10_us_companies_data, "organization")
top_10_us_companies_patents <- merge(x = top_10_us_companies_data, y = Q1_data, 
                       by    = "organization",
                       all.x = TRUE, 
                       all.y = FALSE)[,.(organization,patent_id)]
# 3. Join the new table and uspc by patent_id
top_10_us_companies_patents_uspc <- merge(x = top_10_us_companies_patents, y = Q3_uspc_tbl, 
                       by    = "patent_id",
                       all.x = TRUE, 
                       all.y = FALSE)[,.(organization,patent_id,mainclass_id)]
# 5. Merge with maincalsses_current to get info about uspc calsses
Q3_data <- merge(x = top_10_us_companies_patents_uspc, y = mainclass_current, 
                       by.x    = "mainclass_id",
                       by.y    = "id",
                       all.x = TRUE, 
                       all.y = FALSE)
# 6. Group by uspc classes, count entries and order descending including the description of the mainclasses
top_uspc_main_classes <- Q3_data[,.N,by = .(mainclass_id,title)][order(-N),.(mainclass_id,title,uspc_usage_by_top_10_US_comp=N)]
```

### View Results
```{r results = "asis"}
options(knitr.table.format = "html") 
kbl(top_uspc_main_classes[1:5, ]) %>%
  kable_styling(bootstrap_options = c("striped", "hover"),fixed_thead = T)
```

## Writing Files
### RDS
```{r eval=FALSE} 
Q1_data %>% 
  write_rds("~/Documents/GitHub/ws20-business-data-science-basics---lab-journal-ckz-dev/Manipulated_Data/Data_wrangling/Q1_data.rds")
Q2_data %>% 
  write_rds("~/Documents/GitHub/ws20-business-data-science-basics---lab-journal-ckz-dev/Manipulated_Data/Data_wrangling/Q2_data.rds")
Q3_data %>% 
  write_rds("~/Documents/GitHub/ws20-business-data-science-basics---lab-journal-ckz-dev/Manipulated_Data/Data_wrangling/Q3_data.rds")
```