---
title: "Journal Challenge 2a"
author: "David Hackenberger"
date: "2020-11-026"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 3
    #code_folding: hide
---

# Challange Data Aquisition
# 1. Challange Part 1
We want to compile an overview of drinks based on the liquor gin.
For this we use the online database thecocktaildb and the provided API.

#### Install libraries
```{r}
library(RSQLite)
library(tidyverse)
library(glue)
library(jsonlite)
library(httr)
library(xopen)  
library(data.table)
```

## Website used: 
https://www.thecocktaildb.com
```{r}
TheCocktailDB_home_url <- "https://www.thecocktaildb.com"
#xopen(TheCocktailDB_home_url)
```

## Retrieve data via an API
The API is free to use with an Academic License Key with limited functionality.
Access is via the link: https://www.thecocktaildb.com/api/json/v1/ followed by the license key, the desired database processing, a class and an element.
Example: https://www.thecocktaildb.com/api/json/v1/1/search.php?s=margarita searches a cocktail by name.

Since we can only retrieve limited lists from the database under the free license, we build a function that we execute multiple times and thus combine our own database.

## Define function
```{r}
                    #We will need the following variables:
                    #key    <- 1        # Academic Token
                    #process  <- "filter"   # list, filter, search, lookup
                    #operator  <- "i"      # i: ingredients, i: idDrink, iid: ingrediants by ID
                    #element   <- "Gin"   # "list" oder "Benennung"
thecocktaildb_JSON <- function(key,process,operator,element){
  url <- modify_url(url = TheCocktailDB_home_url, path = glue("/api/json/v1/{key}/{process}.php?{operator}={element}"))
  resp <- GET(url)
  stop_for_status(resp)
}
```

## Building the dataset
First we get a list of contents to check how the spirit Gin is listed in the database.
```{r}
list_of_ingrediants_tbl <- thecocktaildb_JSON(1,"list","i","list") %>%
# Convert
  .$content %>% 
  rawToChar() %>% 
  fromJSON()%>%
  .$drinks %>%
  as_tibble() %>%
  # Renaming
  rename("Ingrediants"       = "strIngredient1")
  
list_of_ingrediants_tbl$Ingrediants
```

Gin is the third entry in the contents list and is spelled "Gin".
Now let's call up a list of all drinks with the ingredient Gin.
```{r}
list_of_Gin_drinks_tbl <- thecocktaildb_JSON(1,"filter","i",list_of_ingrediants_tbl$Ingrediants[3]) %>%
# Convert
  .$content %>% 
  rawToChar() %>% 
  fromJSON() %>%
  .$drinks %>%
  as_tibble() %>%
  #Clean
  select(-strDrinkThumb) %>%
  # Renaming
  rename("Drink"       = "strDrink") %>%
  rename("ID"       = "idDrink")
```

Now we have the titles of the gin drinks and can use there ids to retrieve further information from the database.
```{r}
get_Details <- function(id){
drink_details_tbl <- thecocktaildb_JSON(1,"lookup","i",id) %>% 
  # Convert
  .$content %>% 
  rawToChar() %>% 
  fromJSON() %>% 
  .$drinks %>%
  as_tibble() %>% 
  #Clean
  select(strDrink,idDrink,strCategory,strGlass,
         strInstructions,starts_with("strIngredient"),starts_with("strMeasure"))
}

library(furrr)     # Parallel Processing using furrr (iteration)
plan("multiprocess")

Gin_drinks_tbl <- future_map(list_of_Gin_drinks_tbl$ID, get_Details) %>% 
  rbindlist(use.names=TRUE, fill=FALSE, idcol=NULL) %>% 
  as_tibble()

#Rename, beacuse most of the collums start with str
colnames(Gin_drinks_tbl) = gsub("str", "", colnames(Gin_drinks_tbl))
```

## Resulting Dataset
Now we have an extensive data set of gin drinks with ingredients, recipe and quantities.
```{r results = "asis"}
library(kableExtra)
options(knitr.table.format = "html") 
kbl(Gin_drinks_tbl[1:10, ]) %>%
  kable_styling(bootstrap_options = c("striped", "hover"),fixed_thead = T) %>%
  column_spec(5, width = "30em") %>% 
  scroll_box(width = "100%", height = "400px")
 
```
## Writing Files

### RDS
```{r}
Gin_drinks_tbl %>% 
  write_rds("~/Documents/GitHub/ws20-business-data-science-basics---lab-journal-ckz-dev/Manipulated_Data/Data_aquisition/Gin_drinks.rds")
```

# 2. Challange Part 2
## Question
We want to build a dataset buy web scapping from the Rosebike webshop.
The scope is a database with the model names and prices, not just for one category but for all products.
#### New libraries
```{r}
library(rvest)
library(stringi)   # character string/text processing
```
We can use the selector Gadget to get more information about the website structure.
#### get css /x path selector Gadget, run in searchbar
```{r eval=FALSE}
javascript:(function()%7Bvar%20s=document.createElement('div');s.innerHTML=
              'Loading...';s.style.color='black';s.style.padding='20px';s.style.position=
              'fixed';s.style.zIndex='9999';s.style.fontSize='3.0em';s.style.border=
              '2px%20solid%20black';s.style.right='40px';s.style.top='40px';s.setAttribute
            ('class','selector_gadget_loading');s.style.background='white';document.body.appendChild(s);s=
              document.createElement('script');s.setAttribute('type','text/javascript');s.setAttribute
            ('src','https://dv0akt2986vzh.cloudfront.net/unstable/lib/selectorgadget.js');document.body.appendChild(s);%7D)();
```

## Get URLs for product categories
The categories can be scapped from the navigation bar at the top right and acessed via the titles.

```{r}
url_home          <- "https://www.rosebikes.de"
#xopen(url_home) # Open links directly from RStudio to inspect them

# Read in the HTML for the entire webpage
html_home         <- read_html(url_home)

# Web scrape the categroies
bike_category_url_tbl <- html_home %>%

  # Get the nodes for the families with the title description. The pointer is unique for bicycle categories.
  html_nodes(css = ".main-navigation-category-with-tiles__item > a") %>% 
  # ...and extract the information of the href
  html_attr("href") %>% 

  # Remove the product categorie sale because these bikes are parrt of other categoreis as well
  #discard(.p = ~stringr::str_detect(.x,"e-bike")) # the webiste was adapted and it stoped working, thereofre we are only continuing with the first 5 categories.
  .[1:5] %>% 

  # Convert vector to tibble
  enframe(name = "position", value = "subdirectory") %>% 
  as_tibble() %>% 
  
  # Create a additinal collumn to store the url to each sub-page
  mutate(url = glue("{url_home}{subdirectory}"))
```

## Get URLs for product families
Now we have a tbl with the url links to each product category. From there we can get the product families which contain the bike models.
For that we set up a function that gets the families the same way as we got the categories for each category.

```{r}
#Function to get the subdirectories for the bike families
get_bike_family_subd <- function(url) {
  html_bike_family <- read_html(url)
  bike_category_family_tbl <-  html_bike_family %>% 
  html_nodes(css = ".catalog-category-bikes__list-item > div > a") %>% 
  html_attr("href") %>% 
  # Convert vector to tibble
  enframe(name = "position_cf", value = "subdirectory_cf") %>% 
  as_tibble()
               
}
```
Mapping the function with every bike category
Alternative 1: with the map function (it ran before and nor gets a pare error, therefore alternative 2)
```{r eval=FALSE}
bike_family_url_tbl <- map(bike_category_url_tbl$url,get_bike_family_subd) %>% 
  # Unpack the mapped list and convert it to a tibble
  rbindlist(use.names=TRUE, fill=FALSE, idcol=NULL) %>% 
  as_tibble() %>% 
  # create a extra collumn to store the link to each product family page
  mutate(url = glue("{url_home}{subdirectory_cf}")) %>% 
  # organize
  select(url,subdirectory_cf) %>% 
  # convert glue to char
  mutate(url = as.character(url))
```
Alternative 2: manually
```{r}
bike_family_url_tbl_1 <- get_bike_family_subd(bike_category_url_tbl$url[1]) 
bike_family_url_tbl_2 <- get_bike_family_subd(bike_category_url_tbl$url[2]) 
bike_family_url_tbl_3 <- get_bike_family_subd(bike_category_url_tbl$url[3])
bike_family_url_tbl_4 <- get_bike_family_subd(bike_category_url_tbl$url[4])
bike_family_url_tbl_5 <- get_bike_family_subd(bike_category_url_tbl$url[5])

bike_family_url_tbl <- rbind(bike_family_url_tbl_1, bike_family_url_tbl_2,bike_family_url_tbl_3,bike_family_url_tbl_4,bike_family_url_tbl_5) %>% 
  as_tibble() %>% 
  # create a extra collumn to store the link to each product family page
  mutate(url = glue("{url_home}{subdirectory_cf}")) %>% 
  # organize
  select(url,subdirectory_cf) %>% 
  # convert glue to char
  mutate(url = as.character(url))
```

## Excess product data
Now its time to excesses each product family page and gather the information about the different product variations. Each bike may have more than one variation to buy it, which have a different name and price of course.
For this, we set up a function that builds the dataset step by step from each url we collected before.

```{r}
# function to gather information about the product variatinos
get_bike_info <- function(url,subd) {
  # read each family page
  html_bike_model <- read_html(url)
  # get the names of the different variants
  bike_info_names_tbl <-  html_bike_model %>% 
      # the info is stored in the box title again
      html_nodes(css = ".catalog-category-model__title") %>%
      # get the text
      html_text() %>% 
      # get rid of unwanted characters
      str_remove(pattern = "\n") %>% 
      str_remove(pattern = "\n") %>% 
      # convert to list
      enframe(name = "position", value = "model") %>% 
      # Convert vector to tibble
      as_tibble()
  
  # get the prices for each variant in the same way as we got the names
  bike_info_price_tbl <- html_bike_model %>% 
    html_nodes(css = ".product-tile-price__current-value.catalog-category-model__price-current-value") %>% 
    html_text() %>% 
    str_remove(pattern = "\n") %>% 
    str_remove(pattern = "\n") %>%
    enframe(name = "position", value = "price") %>% 
    # Convert vector to tibble
    as_tibble() %>% 
    # Converts prices from strings to integers for later calculations
    #Convert € strg to numeric value
    mutate(price = gsub("\\.","",price),price = gsub(",00","",price),price = gsub("€","",price),price = as.numeric(price))
  
  # Creating a dataset putting together Category, Family, Model, price, url
  bike_model_collected_info_tbl <- left_join(bike_info_names_tbl,bike_info_price_tbl,by = "position") %>% mutate(link = url, Category_Family = subd) %>% 
    # to get the category and family we seperate the subdirectory wich is seperated by /
    separate(col = Category_Family, into = c("category_1","category_2","category","family"),
        sep = "/",extra = "drop") %>% 
    # get rid of unwanted cahacters
    mutate(family = gsub("\\-", "",family))
  
  # asaamble the dataset
  bike_model_info_tbl <-   bike_model_collected_info_tbl %>% 
    # Delet unessesarry columns 
    select(-position,-category_1,-category_2) %>% 
    #Restructure
    select(category,family,model,price,link)
    
}
```

## Test the function
Test for one
```{r}
bike_model_info_tbl_1 <- get_bike_info(bike_family_url_tbl$url[1],bike_family_url_tbl$subdirectory_cf[1])
```

## Assamble dataset
As this works we can use the function to get the information for every product.
```{r}
library(furrr)
plan("multiprocess")
# Future_map2 to map over several inputs
rose_bike_products_tbl <- future_map2(bike_family_url_tbl$url,bike_family_url_tbl$subdirectory_cf,get_bike_info) %>% 
  rbindlist(use.names=TRUE, fill=FALSE, idcol=NULL) %>% 
  as_tibble()
```

## Resulting Data
```{r results = "asis"}
options(knitr.table.format = "html") 
kbl(rose_bike_products_tbl[1:10, ]) %>%
  kable_styling(bootstrap_options = c("striped", "hover"),fixed_thead = T) %>%
  column_spec(3, width = "30em") %>% 
  column_spec(5, width = "50em") %>% 
  scroll_box(width = "100%", height = "400px")
```

## Writing Files
### RDS
```{r}
rose_bike_products_tbl %>% 
  write_rds("~/Documents/GitHub/ws20-business-data-science-basics---lab-journal-ckz-dev/Manipulated_Data/Data_aquisition/rose_bike_products.rds")
```


















